Rarefied Null Models

### 2021-04-08 analysis/03_rarefy_null_models.Rmd
Reordering of scripts to add null model script

Get sample dataframe
```{r}
future::plan(multiprocess, workers = 30)
sample_occurrence <- future_map(files, get_plot_sample, n = 500, 
                                .options = furrr_options(seed = TRUE)) #%>%
  # bind_rows() %>%
  # replace(is.na(.), 0)
```
Figure out which samples didn't get null samples
```{r}
null_files <- list.files(here::here("data", "null_samples")) %>%
  paste0(here::here("data", "null_samples"), "/", .)

@@

@@

  print(head(sample_species_mat))
  trait_mat <- get_traitMat(colnames(sample_species_mat), trait_data = traits)

@@

@@

  means <- data %>%
    select(-rarefyid, -richness) %>%
    summarise(across(everything(), mean)) %>%
    pivot_longer(cols = -year, names_to = "metric", values_to = "mean")

  sds <- data %>%
    select(-rarefyid, -richness) %>%
    summarise(across(everything(), sd)) %>%
    pivot_longer(cols = -year, names_to = "metric", values_to = "sd")

  stats <- left_join(means, sds, by = c("year", "metric")) %>%
    left_join(data %>% select(year, rarefyid, rarefy_resamp, richness) %>% distinct(), by = "year") %>%
    mutate(se = sd/sqrt(n),
           lowerCI = mean - qt(0.975, n - 1) * se, 
           upperCI = mean + qt(0.975, n - 1) * se)  %>%
    select(year, rarefyid, everything())

@@

plan(multiprocess)
null_table <- future_map_dfr(null_files, process_nulls, n = 500)

>>>>

Get sample dataframe
```{r}
future::plan(multiprocess, workers = 30)
sample_occurrence <- future_map(files, get_plot_sample, n = 500, 
                                .options = furrr_options(seed = TRUE)) #%>%
  # bind_rows() %>%
  # replace(is.na(.), 0)
```

Figure out which samples didn't get null samples
```{r}
null_files <- list.files(here::here("data", "null_samples")) %>%
  paste0(here::here("data", "null_samples"), "/", .)

@@

  plot_samples %>% select(rarefyid, rarefy_resamp) %>% distinct() %>% print()

@@

  #print(head(sample_species_mat))
  trait_mat <- get_traitMat(colnames(sample_species_mat), trait_data = traits)

@@

Figure out which nulls still need to be calculated
```{r}
null_files <- dir(here::here("data", "null_samples"), "*.csv") 
null_files <- as.data.frame(null_files) %>%
  mutate(rarefyid = str_match(null_files, "(.*?)\\s*_samp")[,2],
         rarefy_samp = str_match(null_files, "samp\\s*(.*?)\\s*.csv")[,2])

fd_files <- dir(here::here("data", "fd_null_output"), "*.tsv")
fd_files <- as.data.frame(fd_files) %>%
  mutate(rarefyid = str_match(fd_files, "null_rarefy\\s*(.*?)\\s*samp")[,2],
         rarefy_samp = str_match(fd_files, "samp\\s*(.*?)\\s*.tsv")[,2])

missing_files <- null_files %>%
  left_join(fd_files) %>% 
  filter(is.na(fd_files)) %>%
  pull(null_files) %>%
  paste0(here::here("data", "null_samples/"), .)

get_nullplot_FD_safe <- possibly(get_nullplot_FD, otherwise = data_frame())
plan(multiprocess, workers = 120)
null_FD <- future_map_dfr(missing_files, ~get_nullplot_FD_safe(.x, traits = trait_ref),
                           .options = furrr_options(seed = TRUE))
```

@@

  means <- data %>%
    select(-rarefyid, -richness, -rarefy_resamp) %>%
    summarise(across(everything(), ~mean(.x, na.rm = TRUE))) %>%
    pivot_longer(cols = -year, names_to = "metric", values_to = "mean")

  sds <- data %>%
    select(-rarefyid, -richness, -rarefy_resamp) %>%
    summarise(across(everything(), ~sd(.x, na.rm = TRUE))) %>%
    pivot_longer(cols = -year, names_to = "metric", values_to = "sd")

  stats <- left_join(means, sds, by = c("year", "metric")) %>%
    left_join(data %>% select(year, rarefyid, rarefy_resamp, richness) %>% distinct(), by = "year") %>%
    mutate(se = sd/sqrt(n),
           lowerCI = mean - qt(0.975, n - 1) * se, 
           upperCI = mean + qt(0.975, n - 1) * se)  %>%
    select(year, rarefyid, rarefy_resamp, everything())

@@

plan(multiprocess, workers = 120)
null_table <- future_map_dfr(null_files, process_nulls, n = 500)
